My title

### 2024-10-11 paper/paper.qmd
Added code for model generation

```{r}
#| warning: false
#| message: false
filtered_df <- df |> filter(year==2021) |> filter(age!=996) |> filter(marstat!=99) |> filter(!educ %in% c(996,997,998,999))
labeled_df <- filtered_df |> mutate(
  label_outcome = if_else(outcome==1, "Yes", "No"),
  label_outcome = as_factor(label_outcome),
  label_sex = if_else(sex==1,"Male", "Female"),
  label_education = case_when(
      educ==100~"Grade 12 or less, no high school diploma or equivalent",
      educ==101~"Grade 8 or less (no further detail)",
      educ==102~"Never attended/kindergarten only",
      educ==103~"Grades 1-11 (no further detail)",
      educ==104~"Grade 1",
      educ==105~"Grade 2",
      educ==106~"Grade 3",
      educ==107~"Grade 4",
      educ==108~"Grade 5",
      educ==109~"Grade 6",
      educ==110~"Grade 7",
      educ==111~"Grade 8",
      educ==112~"Grade 9-12, no diploma (no further detail)",
      educ==113~"Grade 9",
      educ==114~"Grade 10",
      educ==115~"Grade 11",
      educ==116~"12th grade, no diploma",
      educ==200~"High school diploma or GED",
      educ==201~"High school graduate",
      educ==202~"GED or equivalent",
      educ==300~"Some college, no 4yr degree",
      educ==301~"Some college, no degree",
      educ==302~"AA degree: technical/vocational/occupational",
      educ==303~"AA degree: academic program",
      educ==400~"Bachelor's degree (BA,AB,BS,BBA)",
      educ==500~"Master's, Professional, or Doctoral Degree",
      educ==501~"Master's degree (MA,MS,Med,MBA)",
      educ==502~"Professional (MD,DDS,DVM,JD)",
      educ==503~"Doctoral degree (PhD, EdD)",
      educ==504~"Other degree",
      educ==505~"Professional School or Doctoral degree, topcoded (MD, DDS, DVM, JD, PhD, EdD)"
  ),
  label_education = factor(
    label_education,
    levels=c(
      "Grade 12 or less, no high school diploma or equivalent",
      "Grade 8 or less (no further detail)",
      "Never attended/kindergarten only",
      "Grades 1-11 (no further detail)",
      "Grade 1",
      "Grade 2",
      "Grade 3",
      "Grade 4",
      "Grade 5",
      "Grade 6",
      "Grade 7",
      "Grade 8",
      "Grade 9-12, no diploma (no further detail)",
      "Grade 9",
      "Grade 10",
      "Grade 11",
      "12th grade, no diploma",
      "High school diploma or GED",
      "High school graduate",
      "GED or equivalent",
      "Some college, no 4yr degree",
      "Some college, no degree",
      "AA degree: technical/vocational/occupational",
      "AA degree: academic program",
      "Bachelor's degree (BA,AB,BS,BBA)",
      "Master's, Professional, or Doctoral Degree",
      "Master's degree (MA,MS,Med,MBA)",
      "Professional (MD,DDS,DVM,JD)",
      "Doctoral degree (PhD, EdD)",
      "Other degree",
      "Professional School or Doctoral degree, topcoded (MD, DDS, DVM, JD, PhD, EdD)"
    )
  )
)

labeled_df |>
  ggplot(aes(x = label_education, fill = label_outcome)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(label_sex)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Mental Depression"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "bottom")
```

```{r}
#| warning: false
#| message: false
labeled_df_reduced <- labeled_df |> slice_sample(n = 1000)
mental_illness <-
  stan_glm(
    label_outcome ~ label_sex + label_education,
    data = labeled_df_reduced,
    family = binomial(link = "logit"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = 
      normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )
saveRDS(
  mental_illness,
  file = here::here("models/mental_illness.rds")
)
```
```{r}
#| warning: false
#| message: false
mental_illness <- readRDS(file = here::here("models/mental_illness.rds"))

modelsummary(
  list(
    "Mental Illness Exist" = mental_illness
  ),
  statistic = "mad"
  )
```
# Introduction

@@

# Appendix {-}

>>>>

```{r}
#| warning: false
#| message: false
labeled_df |>
  ggplot(aes(x = label_education, fill = label_outcome)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(label_sex)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Mental Depression"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "bottom")
```
```{r}
#| warning: false
#| message: false
mental_illness <- readRDS(file = here::here("models/mental_illness.rds"))

modelsummary(
  list(
    "Mental Illness Exist" = mental_illness
  ),
  statistic = "mad"
  )
```

# Introduction

@@

# Appendix {.unnumbered}
